Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-26 astronum_2018/astronum-xrb.tex
better caption

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{xrb}
\caption{\label{fig:xrb} Helium flame spreading across the surface of
  a neutron star.  Shown are temperature (top), the velocity out of the
  simulation plane (middle), and nuclear energy generation rate
  (bottom).
  The out of plane velocity contours indicate where the Coriolis force
  has created a hurricane-like wind structure which confines the flame,
  leading to an inclined front. It is at such an interface that the
  temperature and burning rate are highest.
  }
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{xrb}
\caption{\label{fig:xrb} Helium flame spreading across the surface of
  a neutron star.  Shown are temperature (top), the nuclear energy
  generation rate (second), the velocity out of the simulation plane
  (third) and the mean molecular weight of the ash (bottom).  The out
  of plane velocity contours indicate where the Coriolis force has
  created a hurricane-like wind structure which confines the flame,
  leading to an inclined front. It is at such an interface that the
  temperature and burning rate are highest.  }
\end{figure}

Figure~\ref{fig:xrb} shows a snapshot in time
